Formal Commutative Algebra in Coq: \\ Nakayama's Lemma\thanks{Source code for this work is available on the following site: \url{https://github.com/ku-sldg/algebra}}

### 2022-11-03 nakayama/paper.tex
Updates to math background, and references added

\title{%Formalizing 
Theoretical Commutative Algebra in Coq: \\ Nakayama's Lemma}

%\thanks{}
\date{}

%\author{}
%\address{}
%\email{}

@@

\emily[inline]{Any suggested changes to the current title are welcome.  Moreover, different fields have different standards for style, etc., so feel free to update prose/citations as appropriate. }
\emily[inline]{Add link to github for code?}

@@

The mathematical field of \emph{commutative algebra} stems from the study of solutions to polynomial equations, and now centers around \emph{commutative rings}, i.e., rings whose multiplication satisfies the commutative law, \emph{ideals} of these rings, and \emph{modules} over them. 
Commutative algebra has broad applications to science and technology, including in the field of robotics, and the study of the human genome.
The commutative-algebraic notion of a Gr\"obner basis, a special type of generating set for an ideal in a ring of polynomials, has become a fundamental computational tool in 
coding theory and cryptography (e.g., see  \cite{grobner-bases-cryptography}).
A implementation of Buchberger's algorithm \cite{buchberger} for determining 
Gr\'obner bases of ideals in polynomial rings has been proved correct within the proof assistant Coq \cite{the_coq_development_team_2019_3476303,thery-buchberger}, and an integrated formal development of the algorithm in Coq has also been carried out \cite{persson2001integrated} (see also \cite{grobner-type-theory}).

@@

\section{Mathematical basis and motivation}

In abstract algebra, the quintessential example of a \emph{commutative ring} is the collection of all integers \[\mathbb{Z} = \{ \ldots, -3, 2, -1, 0, 1, 2, 3, \ldots \}\]
One can add or multiply any two integers to obtain another, both of these binary operations satisfy the associative and commutative laws, and the distributive law governing their compatibility holds.

In general, a ring is a set $R$ with two binary operations, which we call \emph{addition} and \emph{mutiplication}, typically denoted $\cdot$ and $+$, respectively.  Under addition, $R$ must be an abelian group, meaning that addition satisfies the associative and commutative laws, and $R$ must contain an additive identity and negatives, i.e., there exists an element $0 \in R$ such that for all $r \in R$,  $r+0 = r$  and there exists an element denoted $-r$ in $R$ for which $r + (-r) = 0$.
Moreover, multiplication must satisfy the associative law, and the distributive law on the compatibility of addition and multiplication must hold, i.e., for all $r, s, t \in R$, $r \cdot (s+t) = (r \cdot s)  + (r \cdot t)$ and $(r+s)\cdot t = (r \cdot t) + (s \cdot t)$.

%$R$ must have an multiplicative identity, an element $1 \in R$ such that $1 \cdot r = r \cdot 1 = r$ for every $r \in R$, .  Finally, the

The

An \emph{ideal} of commutative ring $R$ is a subset $I$ of $R$ that is itself

@@

@@

>>>>

\title{ 
Formal Commutative Algebra in Coq: \\ Nakayama's Lemma\thanks{Source code for this work is available on the following site: \url{https://github.com/ku-sldg/algebra}}
}

\date{}

%\author{}
\author{

	Authors

	\vspace{.2cm}

	\\

	Institute for Information Sciences \\
	The University of Kansas \\
	Lawrence, KS 66045}
%\email{}

%\thanks{Witt acknowledges support from NSF CAREER Award DMS-1945611 and the 2022-23 Ruth I.\, Michler Memorial Prize from the Association for Women in Mathematics.}

@@

\noindent \textbf{Keywords:}
Formalization of Mathematics,
Formal Proof,
Commutative Algebra,
Commutative Ring,
Ideal,
Module over a Ring.

@@

The mathematical field of \emph{commutative algebra} stems from the study of solutions to polynomial equations.  Research in the field now centers around \emph{commutative rings}--rings in which order does not affect multiplication, i.e., $x \cdot y = y \cdot x$ for any ring elements $x$ and $y$--and fundamental algebraic objects associated to them:  \emph{ideals} of these rings, and \emph{modules} over them. 
Commutative algebra has deep connections with other areas of theoretical mathematics, including number theory and algebraic geometry.

Commutative algebra also has broad applications to science and technology.  For instance, it has been integral to advances in robotics \cite{cox-little-oshea}, and has helped form our current understanding of the human genome \cite{genetic-algebra}. 
The commutative-algebraic notion of a Gr\"obner basis, a special type of generating set for an ideal in a ring of polynomials, has become a fundamental computational tool in 
coding theory and cryptography (e.g., see  \cite{grobner-bases-cryptography}).
A implementation of Buchberger's algorithm \cite{buchberger} for determining 
Gr\"obner bases of ideals in polynomial rings has been proved correct within the proof assistant Coq \cite{the_coq_development_team_2019_3476303,thery-buchberger}, and an integrated formal development of the algorithm in Coq has also been carried out \cite{persson2001integrated} (see also \cite{grobner-type-theory}).

@@

\section{Mathematical Basis and Motivation}

\subsection{The Fundamental Algebraic Objects}

\emily[inline]{Something about building up a lot}

\paragraph{Commutative rings.}
In abstract algebra, the quintessential example of a commutative ring is the set of integers
\[\mathbb{Z} = \{ \ldots, -3, -2, -1, 0, 1, 2, 3, \ldots \}.\]
using the natural definitions of addition and multiplication.

Adding two integers produces another, and the associative and commutative laws hold for addition.  The integers form an \emph{abelian group} under addition since $0 \in \mathbb{Z}$ is the \emph{additive identity} in the sense that adding zero has no effect on any integer, and given any integer $n$, the integer $-n$ is its \emph{additive inverse} in the sense that the sum of $n$ and $-n$ is the additive identity $0$.

The set of integers also forms a \emph{ring} because it is closed under multiplication, which again satisfies associativity, and the distributive law governing the compatibility of addition and multiplication holds. 
Even more, the integers form a 
\emph{commutative ring} since $n \cdot m = m \cdot n$ for all integers $n$ and $m$.  Moreover,  the integer $1$ is the ring's \emph{multiplicative identity}, since for any  $n \in \mathbb{Z}$ one has $n \cdot 1 = 1 \cdot n = n$, $\mathbb{Z}$ is, furthermore, a \emph{commutative ring with identity}.

In general, a \emph{ring} is a set $R$ with two binary operations, which we call \emph{addition} and \emph{mutiplication}, typically denoted $\cdot$ and $+$, respectively.  As motivated by the properties of the ring of integers, addition, $R$ must be an abelian group, multiplication must be associative, and the distributive law must hold, i.e., for all $x, y, z \in R$, $(x+y)\cdot z = x \cdot z + y \cdot z$ and $x \cdot (y+z) = x \cdot y + x \cdot z$.

\emily[inline]{Quickly mention familiar examples}

We will use $0$ to refer to an additive identity, and $1$ will represent a multiplicative identity.

Rather than call upon the \emph{Mathematical Components Library} 
 for Coq \cite{mathcomp}

\paragraph{Ideals.}
The concept of an {ideal} of a ring can be thought of as an extension of the notion of an integer $x$ in the ring of integers $\mathbb{Z}$. 
An \emph{ideal} of commutative ring $R$ is a subset $I$ of $R$ that is itself 
an abelian group under addition,  
which satisfies the following ``absorption'' property: Given any element $a$ of $I$, 
the product  $x \cdot a$ is again in $I$ for any ring element $x \in R$.

One can verify that given any integer $n$, the set $n\mathbb{Z}$ of its multiples forms an ideal of $\mathbb{Z}$.  For instance, $2 \mathbb{Z}$ consists of all even numbers, and is an abelian group under addition: the sum of two even numbers is even, the additive identity $0$ is eve, and the negative of an even number is even.
Moreover, the absorption property holds since the product of any integer and an even number is again even. 
In fact, every ideal of the ring of integers has this form $n\mathbb{Z}$ for some integer $n$, though ideals in general commutative rings can have more complicated properties.

Since every integer $n$ can be written as $1 \cdot n$, the ideal $1 \mathbb{Z}$ is the entire ring $\mathbb{Z}$.   One can see that given a commutative ring $R$ itself satisfies the axioms required to be an ideal of $R$.  We call an ideal $I$ of $R$ \emph{proper} if it is strictly contained in $R$.  Every commutative ring with unity contains the proper ideal consisting solely of the additive identity $0$.

A \emph{maximal ideal} of a commutative ring is a proper ideal that is maximal with respect to inclusion, i.e., no other proper ideal strictly contains it. 
Going back to the ring of integers, $6 \mathbb{Z} \subsetneq 2 \mathbb{Z}$ since every multiple of $6$ is even, 
so $6 \mathbb{Z}$ is not a maximal ideal of $\mathbb{Z}$. 
However, no proper ideal $I$ contains $2 \mathbb{Z}$:  If $2 \mathbb{Z}\subsetneq I \subsetneq \mathbb{Z}$, then $I$  would necessarily contain an odd number $n$.  Writing $n=2k+1$ for some integer $k$, we notice that since $-2k = 2 \cdot -k$  is in $2\mathbb{Z}$, it is also an element of the larger set $I$, and since $I$ is an abelian group under addition, $(2k+1) + $

In fact, $3 \mathbb{Z}$

\subsection{Nakayama's Lemma, Informally}

@@

\subsection{Our Algebraic Hierarchy}

@@

\section{Formally Proving Nakayama's Lemma}
